\vspace{60pt}\\ \huge \bfseries Skedge \\ \vspace{10pt} \Large Smarter course scheduling for our University

### 2016-04-13 design/modernity.tex
little updates
done

\begin{figure}[ht]
  \centering
    \fbox{
      \includegraphics[width=10cm]{images/cdcs/2010}
    }
  \caption{CDCS in July 2, 2010, virtually unchanged from today, courtesy of \emph{Archive.org}}
  \label{fig:cdcs2010}
\end{figure}

@@

\item Skedge accommodates a schedule into its design, whereas Better CDCS has to work around an interface that wasn't designed with one. As a result, Better CDCS has lower usability, requiring the user to toggle between search results and their schedule. Skedge, conversely, gives users immediate visual feedback on how a course would fit into their schedule.

\item Schedule data is centralized on Skedge's servers as opposed to locally in a browser cache, meaning that it can synchronize across a user's devices or in sessions on public computers, persists browser resets, and can be easily publicly shared to other users.

\item Extensions like Better CDCS have limited browser support. Internet Explorer and mobile browsers are unsupported, for example.
\end{enumerate}

>>>>

\begin{figure}[ht]
  \centering
    \fbox{
      \includegraphics[width=10cm]{images/cdcs/2010}
    }
  \caption[CDCS in July 2, 2010]{CDCS in July 2, 2010, virtually unchanged from today, courtesy of \emph{Archive.org}}
  \label{fig:cdcs2010}
\end{figure}

@@

\item Skedge was designed to have a schedule, whereas Better CDCS works within an interface that wasn't. CDCS suffers lower usability as a result, requiring toggle between results and schedules. Skedge, conversely, immediately projects a course into the user's schedule.

\item Schedule data is centralized on Skedge's servers as opposed to locally in a browser, meaning that it can synchronize across a user's devices and can be easily publicly shared to others.

\item Extensions like Better CDCS have limited browser support. Internet Explorer and mobile browsers are unsupported, for example.

\item As separate systems trying to deliver one cohesive experience, Better CDCS and CDCS are dependent on each other. If the format of one changes, the other is likely to break.
\end{enumerate}

### 2016-04-13 introduction.tex
done

This paper will begin by

@@

CDCS is the University's official tool for

\label{fig:cdcs-index}

@@

@@

Skedge is a website on which I started rapid development on December 9th 2013, and have been developing it on and off since.

Bookmarks

Students, parents, department coordinators, and faculty can all benefit from such tool improvements.

user accounts are lightweight, no login, cookie (browser) based

\ref{fig:sk-index}

\begin{figure}[ht]
    \centering
        \begin{subfigure}[h]{14cm}
            \centering
            \fbox{
                \includegraphics[width=1.00\textwidth]{images/cdcs/index}
            }
            \caption{CDCS, with the search query {\tt csc}}
            \label{fig:cdcs-index}
        \end{subfigure}\\
        \vspace{10pt}\\
        \begin{subfigure}[h]{14cm}
            \centering
            \fbox{
                \includegraphics[width=1.00\textwidth]{images/cdcs/better}
            }
            \caption{Better CDCS, a separate browser extension that embeds buttons into the CDCS course results interface, allowing users to add courses to a locally-stored schedule}
            \label{fig:cdcs-better}
        \end{subfigure}
    \caption{CDCS and Better CDCS in their current states}
\end{figure}

\begin{figure}[ht]
    \centering
    \fbox{
        \includegraphics[width=1.00\textwidth]{images/skedge/index}
    }
    \caption[Skedge with the search query {\tt csc}]{Skedge with the search query {\tt csc} and the user's current schedule on the right}
    \label{fig:sk-index}
\end{figure}

>>>>

\vspace{-20pt}

I am proud to finally, officially introduce the world to \emph{Skedge}, a website I have been developing since December 2013. It began as a weekend project after I spent too much time trying to find interesting elective classes, and it wasn't until I briefly presented it at a RocHack ``Hacker Night'' when I realized the potential it had to help others as well. I never expected the subject of my senior thesis to be something so close to my heart, so I am grateful for such a fun and motivating opportunity to continue work on Skedge, and, selfishly, for the outlet of recognition.

@@

\begin{figure}
    \centering
        \begin{subfigure}[h]{14cm}
            \centering
            \fbox{
                \includegraphics[width=1.00\textwidth]{images/cdcs/index}
            }
            \caption{CDCS, with the search query {\tt csc}}
            \label{fig:cdcs-index}
        \end{subfigure}\\
        \vspace{10pt}\\
        \begin{subfigure}[h]{14cm}
            \centering
            \fbox{
                \includegraphics[width=1.00\textwidth]{images/cdcs/better}
            }
            \caption{Better CDCS, a separate browser extension that embeds buttons into the CDCS course results interface, allowing users to add courses to a locally-stored schedule}
            \label{fig:cdcs-better}
        \end{subfigure}
    \caption{CDCS and Better CDCS in their current states}
\end{figure}

``Course Description / Course Schedule,'' (or \emph{CDCS} for short) is the University's official tool for browsing the University's current course catalog \cite{cdcs}.

The CDCS interface consists of a series of form fields for inputting search queries on the left, and search results on the right side (see Figure \ref{fig:cdcs-index}). Despite ``Course Schedule'' being in its name, CDCS does not offer scheduling functionality. Only course times can viewed, and it is up to the user to keep track of the courses they are considering for their next semester.

@@

Better CDCS \cite{better-cdcs} is a browser extension, available for Firefox, Safari, and Chrome, that offers a solution to the lack of scheduling mentioned above. It works by injecting ``Add Section'' and ``Bookmark Section'' buttons into the existing CDCS interface, and providing a tab on top of the screen that will toggle between the user's schedule and the search results (see Figure \ref{fig:cdcs-better}).

@@

\begin{figure}[H]
    \centering
    \fbox{
        \includegraphics[width=1.00\textwidth]{images/skedge/index}
    }
    \caption[Skedge with the search query {\tt csc}]{Skedge with the search query {\tt csc} and the user's current schedule on the right}
    \label{fig:sk-index}
\end{figure}

Skedge \cite{skedge} is, in short, CDCS combined with Better CDCS on a single platform (see Figure \ref{fig:sk-index}). Like CDCS, it is lightweight, service-oriented, and doesn't require a login, but unlike CDCS, it doesn't require a separate browser extension.

It matches feature-for-feature with the two tools (search options, information displayed, scheduling and course bookmarks, etc.), and aims to improve upon the work of both of them on several fronts, which will be investigated in this paper in great detail. It is my contention that students, parents, faculty, staff, and administration can all benefit from such improvements.

\vspace{20pt}

\noindent
This paper is organized in two parts, with a brief intermission in between. First, I will explain many of Skedge's design decisions in relation to what I call my ``grievances'' with CDCS in its current state. The second part will look at collected data, extrapolating how students use Skedge and using several novel metrics to measure its usability and effectiveness as a platform.
